---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/vincenzocoia/powers)

__Note__: This R package is not mean to be "serious". It's just for teaching purposes. 

# powers, Box-Cox transform

This is an R package that allows you to compute power functions. You can also compute a [Box-Cox transform](https://en.wikipedia.org/wiki/Power_transform#Box%E2%80%93Cox_transformation).

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("MalcolmNSB/powers")
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example}
powers::reciprocal(2)
powers::square(2)
powers::cube(2)
powers::Box_Cox_transform(c(1,2), c(3,4))
powers::Box_Cox_transform(1,2)
```

## For Developers

(Again, I don't actually intend for anyone to develop this silly package, but if I did, here's what I'd write.)

Use the internal `pow` function as the machinery for the front-end functions such as `square`, `cube`, `reciprocal`, and `Box_Cox_transform`. 
