---
title: "Using the `powers` package"
author: "Vincenzo Coia (modified by Malcolm Bowles)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the `powers` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

__Note__: This package isn't actually meant to be "serious". I made it just for teaching purposes.

Want to compute powers without having to use `^` or `**`? Give `sqrt` some friends by loading the `powers` package! 

```{r}
library(powers)
```

Want squares, cubes, or reciprocals? Easy.

```{r}
square(1:10)
cube(1:10)
reciprocal(1:10)
```

Need to apply a [Box-Cox transform](https://en.wikipedia.org/wiki/Power_transform#Box%E2%80%93Cox_transformation)  to your data? You can do that too!
```{r}
Box_Cox_transform(1:10, 2)
Box_Cox_transform(1:10, c(1,2))
```


`apply`-family friendly, too! (Box-Cox transform excluded.)

```{r}
my_list <- list(1:10, 0.5, -0.7)
## So base-R-boring!
lapply(my_list, function(x) x^2)
## Use powers instead!
lapply(my_list, square)
```

It even comes with the ability to display its output in plot form! (Box-Cox transform excluded.)

```{r}
reciprocal(1:10, plot_it=TRUE)
```

Wow!!!
